SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] editing Malinova mitigation

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover. By \textsf(1) funding the \textit{commitment address}, user is committed to the unlock transaction. In the reveal phase, \textsf(2) user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction. \textsf(3) Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. \textsf(4) Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

@@

% Jeremy: This needs some clarification; what exactly is the principle they are applying???
Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Specifically they use economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved using ECDSA ECRecover. By \textsf(1) funding the \textit{commitment address}, user is committed to the unlock transaction. In the reveal phase, \textsf(2) user sends the \textit{reveal transaction} to the DApp, revealing the nature of the commitment transaction. \textsf(3) Then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. \textsf(4) Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

@@

% Jeremy: This needs some clarification; what exactly is the principle they are applying???
%Shayan: Is this better? they basically use economical model for welfare of the traders in a transparent environment. To extend the idea more, we need to dive in their economical model which I think is out of scope of this paper.
Malinova and Park discuss different design setting for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}. They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers. To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
